\PaperTitle

### 2024-05-04 Final_Report/paper.tex

\subsection{Data Preparation and Processing}
To maintain normalized representation in all the collected datasets, a process of data harmonization 
was applied after collecting the necessary data. The dataset with the minimum number of observations is identified and accounted for when
truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models.

\subsubsection{Feature Selection}

\subsubsection{Data Formatting}

>>>>

\subsection{Data Preparation and Processing}
In order to ensure the integrity and reliability of our models,
the collected data must be processed prior to model training.

\subsubsection{Feature Selection}
The data collection process using Wireshark yields a dataset containing seven distinct features shown in Figure 2. 
\begin{itemize}
  \item \textbf{Packet Number}: An integer representing the order in which the packets were captured during the Wireshark session. Provides insight on the order of the packets on the network interface. 
  \item \textbf{Time}: A floating point value representing the relative timestamp for each packet since the start of the Wireshark session. Similar to packet number, the time feature provides a better understanding of the packet order yet is more precise.
  \item \textbf{Source}: A string value containing the internet protocol address of the device that the packet originated from. 
  \item \textbf{Destination}: A string value containing the internet protocol address of the device that is receiving the packet. 
  \item \textbf{Protocol}: A string value which contains the network protocol employed for the transmission of the packet. Three distinct protocols were identified within the datasets used in this project (QUIC, TCP and TLSv1.2).
  \item \textbf{Length}: An integer representing the size of a packet in bits 
  \item \textbf{Info}: A string value containing more information pertaining to a packet. This value can vary heavily between packets.
\end{itemize} 
As the objective of this project is to predict the origin of web traffic, both source and destination are excluded from the dataset used to train the models. 
Similairly, the "info" feature is also removed from our train data as further testing revealed that the feature led to extraneous noise in our dataset. 
Consequently, the features selected for training and testing the models are Time, Length, and Protocol. The Protocol feature is converted to an integer for compatibility with 
the models using a dictionary to map protocol names to a corresponding numerical representation (e.g., 'TCP': 0, 'QUIC': 1, 'TLSv1.2': 2) as shown in Figure 3.  Additionally, a categorical variable titled "Website" 
is created which displays which website the packet originated (e.g., LinkedIn, ChatGPT, Blackboard). The "Website" feature acts as the target variable and allows 
the models to detect relationships between the packets and their corresponding web traffic origin.

\subsubsection{Data Formatting}
To maintain normalized representation in all the collected datasets, a process of data harmonization 
was applied after collecting the necessary data. The dataset with the minimum number of observations is identified and accounted for when
truncating the remaining two datasets. Subsequently, the three datasets are combined and rearranged to minimize bias while training each of our models.
This process ensures a balanced yet unbiased dataset that maximizes the effectiveness of our models. Figure 3 pesents the refined data following the data preparation. 
\begin{figure}[htp] % h: here, t: top, p: bottom
  \centering
  \includegraphics[width=0.5\textwidth]{Figures_and_Graphs/fullDataDiagram.png}
  \caption{Processed Web Traffic Data}
  \label{fig:wireshark}
\end{figure}
